### 2012-09-01 sections/introduction.tex
* implementation   * flow query intermediate format     * custom c library to read flow records     * dedicated functions for each kind of operation   * execution workflow     * faster filter (with graph)     * grouper implementation       * possible grouping approaches       * faster grouping in generic case (nested bsearch)       * faster grouping in specific case (no bsearch needed) (with graph)       * cooked netflow v5 records for group aggregations     * group filter implementation     * merger implementation       * merger iterator utility       * skipping iterator permutations on sorte

@@

\cleardoublepage

>>>>

Researchers, service providers and security analysts have long been interested
in network and user behavioral patterns of the traffic crossing the internet
backbone. They want to use this information for the purpose of billing and
mediation, bandwidth provisioning, detecting malicious attacks, network
performance evaluation and overall improvement. Traffic measurement techniques
that have been rapidly evolving in the last decade, have matured enough today
to provide such an insight.

Flow capture today, has emerged out to be one of the favored network
measurement techniques. This has largely been due to the reduction in the
monitoring traffic at the flow-level and the fine-grained control which was
not previously possible using SNMP interface-level queries. As a result,
each networking vendor has tried to come up with a standard protocol that
defines the semantics of this flow export. In this pursuit, Cisco eventually
managed to make their proprietary protocol so ubiquitously available, that the
next-generation universal standard is based on it.

@@

### 2012-09-01 sections/relatedwork.tex
* introduction   * traffic measurement approach blurb   * flow export protocol blurb * related work   * silk; and how it differs from nfql * performance evaluations   * stressing the filter   * stressing the grouper   * stressing the group filter   * stressing the merger   * stressing the ungrouper * conclusion

>>>>

SiLK\footnote{\url{http://tools.netsa.cert.org/silk/}} is a network traffic
collection and analysis tool developed and maintained by the CERT Network
Situational Awareness Team (CERT NetSA) at Carnegie Mellon University. SiLK is
the tool that comes quite close to providing similar capabilities as provided
by \ac{NFQL} and is therefore used as a reference point to compare the
performance of the \ac{NFQL} execution engine in this paper. The design and
implementation of SiLK, however, differs a lot from that of \ac{NFQL}.For
instance, in SiLK there are separate tools to perform the task of each stage
of the \ac{NFQL} processing pipeline. The stage functionality is not
full-fledged though. The grouping and merging operations can only be performed
using an equality operator. This is assumed in the tool, thereby allowing it
to perform optimization such as using hash tables to perform lookups. There
are also stringent requirements to how flow-data needs to be organized before
it can be piped into a tool. The grouping tool, for instance, assumes that the
to-be supplied input flow data is already sorted on the field column.  These
requirements make it a little cumbersome to design a full-fledged flow query.
For instance, trying to mimic a \ac{NFQL} query in SiLK ends up as a bash
script with over a dozen of SiLK tools piped together.
